Ground state energy of quantum dots using the coupled cluster method

### 2018-05-11 project_2/article/article.tex
First term of amplitude equations

		Now comes the rather tedious task of evaluating all the terms 
		that arises from inserting \autoref{eq:normal_order_expansion}
		into \autoref{eq:doubles_amplitude_1}. The first of such terms
		is
		\begin{equation}
		\begin{aligned}
			\bra{\Phi_{ij}^{ab}} &(F_N + V_N)\ket{\Phi_0} \\
			 =& \sum_{pq}f_{pq}\bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa_q\}\ket{\Phi_0} \\
			 &+\frac{1}{4}\sum_{pqrs}\bra{pq}\ket{rs}
			 \bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa^\dagger_qa_sa_r\}\ket{\Phi_0}
		\end{aligned}
		\end{equation}

>>>>

		Now comes the rather tedious task of evaluating all the terms 
		that arises from inserting \autoref{eq:normal_order_expansion}
		into \autoref{eq:doubles_amplitude_1}. The first of such terms
		is
		\begin{equation}
		\begin{aligned}
			\bra{\Phi_{ij}^{ab}} &(F_N + V_N)\ket{\Phi_0} \\
			 =& \sum_{pq}f_{pq}\bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa_q\}\ket{\Phi_0} \\
			 &+\frac{1}{4}\sum_{pqrs}\bra{pq}\ket{rs}
			 \bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa^\dagger_qa_sa_r\}\ket{\Phi_0}.
		\end{aligned}
		\end{equation}
		The one-electron component does not have any full contractions, while the
		two-electron component produces one contributing integral,
		\begin{equation}
		\begin{aligned}
			\bra{\Phi_{ij}^{ab}} &(V_N)\ket{\Phi_0} \\
				=& \frac{1}{4}\sum_{pqrs}\bra{pq}\ket{rs}
			 \bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa^\dagger_qa_sa_r\}\ket{\Phi_0} \\
			 	=& \frac{1}{4} \sum_{pqrs} \bra{pq}\ket{rs} \\ &\times\Big(
			 		\{ \wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\}
			 		+
			 		\{ \wick{\c1 a^\dagger_i \c2 a^\dagger_j \c4 a_b \c3 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\} \\
			 	  &\ +
			 	 	\{ \wick{\c2 a^\dagger_i \c1 a^\dagger_j \c3 a_b \c4 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\}
			 		+
			 		\{ \wick{\c2 a^\dagger_i \c1 a^\dagger_j \c4 a_b \c3 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\}
			 	\Big) \\
			 	=&  \frac{1}{4} \sum_{pqrs} \bra{pq}\ket{rs} 
			 	( \delta_{ap}\delta_{bq}\delta_{js}\delta_{ir}
			 	 -\delta_{aq}\delta_{bp}\delta_{js}\delta_{ir} \\
			     &\ -\delta_{ap}\delta_{bq}\delta_{jr}\delta_{is}
			 	 +\delta_{aq}\delta_{bp}\delta_{jr}\delta_{is}) = \bra{ab}\ket{ij}.
		\end{aligned}
		\end{equation}
